\LARGE \bf Artificial Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-06-30 paper.tex
Update on Overleaf.

We identify the needed individual and collaborative cognitive skills: geometric
reasoning and situation assessment based on perspective-taking and
affordance analysis; acquisition and representation of knowledge models for
multiple agents (humans and robots, with their specificities); situated,
natural and multi-modal dialogue; human-aware task planning; human-robot
joint task achievement. The article discusses each of these abilities,
presents working implementations, and shows how they combine in a coherent
and original deliberative architecture for human-robot interaction.
Supported by experimental results, we eventually show how explicit knowledge
management, both symbolic and geometric, proves to be instrumental to richer
and more natural human-robot interactions by pushing for pervasive,
human-level semantics within the robot's deliberative system.

>>>>

We identify the needed individual and collaborative cognitive
skills: geometric reasoning and situation assessment based on perspective-taking
and affordance analysis; acquisition and representation of knowledge models for
multiple agents (humans and robots, with their specificities); natural multi-modal dialogue;
human-aware task planning; human-robot joint task achievement. The article
discusses each of these abilities, presents a working implementation, and shows
how they combine in a coherent and original deliberative architecture for
human-robot interaction. Supported by experimental results, we eventually show
how explicit knowledge management, both symbolic and geometric, proves to be
instrumental to richer and more natural human-robot interactions by pushing for
pervasive, human-level semantics within the robot's deliberative system.
